SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 results.tex
small work in results

PPF yields a geometric mean speedup of \textbf{26.95\%} over the
baseline.  This is equivalent to \textbf{4.63\%} over DA-AMPM,
\textbf{4.61\%} over BOP and \textbf{3.78\%} over SPP.  Out of the 95
simpoints developed for SPEC CPU 2017, PPF nearly matches or
outperforms most of the prefetchers on 91 simpoints.  One interesting
case here is {\tt 623.xalancbmk}.  Despite SPP under performing on that
application, PPF manages to considerably outperform all prefetchers.
Since this benchmark has varying prefetch deltas, SPP's conservative
throttling mechanism catches that and quickly halts prefetching at an
average depth of 2.1.  On the other hand, PPF's more efficient
accuracy check enables it to prefetch upto a lookahead depth of
3.3. Doing this, PPF suggests 1.61 times more total prefetches and
2.53 times more useful prefetches than SPP.

@@

\pg{is the following text old? doesn't look right:} At its peak, PPF
manages a speedup of a factor of over \textbf{3.39x} on one of the
{\tt 602.gcc\_s} traces. This also corresponds to speedup gain of
\textbf{60\%} over the next best prefetcher for that trace -- BOP. In
general, benchmarks {\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt
  {623.xalancbmk}\_s}~~and~~{\tt 649.fotonik3d\_s} benefit the most
from PPF, with the speedup over SPP ranging from \textbf{10\% to
  25\%}.

@@

\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the base engine SPP in a multi-core environment
is expected as PPF is a very accurate filter. Thus, it eliminates
useless prefetches before they can cause pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.

>>>>

PPF yields a geometric mean speedup of \textbf{26.95\%} over the
baseline.  This is equivalent to \textbf{4.63\%} over DA-AMPM,
\textbf{4.61\%} over BOP and \textbf{3.78\%} over SPP.  Out of the 20
SPEC CPU 2017 applications, PPF nearly matches or
outperforms all the other prefetchers on 19 applications.  
Benchmarks {\tt 603.bwaves\_s}, {\tt 605.mcf\_s}, {\tt{623.xalancbmk}\_s} 
and {\tt 649. fotonik3d\_s} benefit the most from PPF, with the 
speedup over SPP ranging from \textbf{10\% to 25\%}.

One interesting
case here is {\tt 623.xalancbmk}.  Despite SPP under performing on that
application, PPF manages to considerably outperform all prefetchers.
Since this benchmark has varying prefetch deltas, SPP's conservative
throttling mechanism catches that and quickly halts prefetching at an
average depth of 2.1.  On the other hand, PPF's more efficient
accuracy check enables it to prefetch upto a lookahead depth of
3.3. Doing this, PPF suggests 1.61 times more total prefetches and
2.53 times more useful prefetches than SPP.

@@

% \pg{is the following text old? doesn't look right:} At its peak, PPF
% manages a speedup of a factor of over \textbf{3.39x} on one of the
% {\tt 602.gcc\_s} traces. This also corresponds to speedup gain of
% \textbf{60\%} over the next best prefetcher for that trace -- BOP.

@@

\noindent \textbf{8-Core:} The sorted comparison of speedups on the
memory intensive 8-core mixes is shown in
Figure~\ref{Fig:8Core_SPEC2017}.  PPF improves baseline performance by
\textbf{37.6\%}, an improvement of \textbf{9.65\%} over SPP. For a
random set of SPEC CPU 2017 mixes (not illustrated for space reasons),
PPF improves performance by \textbf{23.4\%} over the baseline,
corresponding to \textbf{4.6\%} over SPP. This increased improvement
achieved by PPF over the base engine SPP in a multi-core environment
is expected as PPF is a very accurate filter. Thus, it eliminates
useless prefetches before they can cause pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive
mixes. This superiority can be attributed to BOP's inherent aggressive
nature. DA-AMPM is also ahead of SPP in both the mixes. Interestingly,
in all these cases, PPF consistently outperforms the best performing
prefetcher.
